### 2013-03-26 doc/final_report/design.tex
Made some crucial changes to the testing chapter and worked in intro and summary

\subsection{ Data Storage }

@@

The preprocessor module is used to annotate and analyse new papers once they 
have been uploaded by the user via the web interface. The preprocessor is designed 
as a daemon which uses pyinotify to hook into the operating system and monitor a directory 
for new papers that have been uploaded. As new papers are detected within the upload directory, 
they are placed into a process queue and the preprocessor analyses them on a first in first out basis.

When a paper is taken from the queue, a series of processes are run upon it to prepare 
it for storage in the database.

\subsubsection{Conversion}

@@

@@

\subsubsection{Type Analysis}

@@

@@

>>>>

@@

The preprocessor module is used to annotate and analyse new papers once they
have been uploaded by the user via the web interface. The preprocessor is
designed as a daemon which hooks into the operating system in order to monitor
a directory for new papers that have been uploaded. As new papers are detected
within the upload directory, they are placed into a process queue and the
preprocessor analyses them on a first in first out basis. When a paper is taken
from the queue, a series of processes are run upon it to prepare it for storage
in the database. These processes are illustrated in Figure
\ref{fig:flow_preprocessor}.

\begin{figure}[!h]
\centering
\includegraphics[width=0.6\textwidth]{images/design/flow_preprocessor.png}
\caption{A flowchart illustrating the preprocessor processes}
\label{fig:flow_preprocessor}
\end{figure}

\subsubsection{PDF Conversion}

The first process in the processing pipeline is conversion of the papers to a
format that can be analysed by SAPIENTA. Currently, SAPIENTA supports the
SciXML\cite{rupp2006flexible} and PubMed Central\cite{pubmedDTD} DTDs. However,
papers stored in PDF format must still be converted in order to be processed.
PDF Files will passed through a routine which extracts text from the paper and
adds the relevant XML tags to make the document SAPIENTA compatible. This
document is then passed forward to the splitter. Papers that are already in a
compatible format are passed forward without any action being taken.

@@

SAPIENTA allocates each sentence within a paper a separate CoreSC label.
However, the sentence boundaries must be detected before the document is passed
into SAPIENTA for annotation. The sentence splitter uses a regular expression
to split the sentences within the document and then adds the necessary
\verb|<s>| tags to the markup to indicate the location of each sentence.

@@

Once the paper has been split, SAPIENTA is used to annotate each sentence with
a relevant CoreSC allocation. These labels are calculated based upon the
sentence's location within the paper as well pairs and triplets of words found
consecutively within the sentence. After this stage, the paper is passed
forwards to be further classified by Partridge.

\subsubsection{Feature Extraction and Classifiers}

The final stage in the preprocessor pipeline is paper classification. During
this stage, features are extracted from the papers and used to classify the
paper in three different ways. The paper's type: case study or review paper
etc. is determined using the presence or absence of different CoreSC labels
within the paper and their relative proportions. The type of paper is
determined by the presence of domain specific nouns and adjectives within the
paper. For example, a biology paper might contain words such as enzyme or amino
acid. The result of the paper, i.e. whether the paper was conclusive and if the
results were positive or negative, are detected through the presence or absense
of words with a strong sentiment polarity as discussed by Wilson et al
(2005)\cite{Wilson05Polarity}. The results from the whole process are then
passed into the data store and saved.

\subsubsection{File Retention and Error Handling}

Each of the independent processes described above generate new files which are
temporarily stored on the server until all of the sub-processes are complete.
Once a paper analysis cycle has finished, the preprocessor triggers a cleanup
operation that removes intermediate files from the system, storing only the
initially uploaded file (which may be a PDF) and the final annotated file in a
permanent location on the filesystem.  The whole analysis process for a single
paper is also wrapped within an error handling block that automatically run the
cleanup routine if something goes wrong. This prevents the system filling up
with invalid files. This mechanism is shown in Figure
\ref{fig:preprocessor_overview}.

\begin{figure}[!h]
\vspace{5mm}
\centering
\includegraphics[width=0.6\textwidth]{images/design/paper_processor_overview.png}
\caption{Preprocessor System Overview}
\label{fig:preprocessor_overview}
\end{figure}

\subsection{ Data Storage }
It is expected that a given Partridge instance may grow in size to contain
thousands of individual papers that have been annotated and are available to
the web backend for inclusion into a user's search results. Reading in and
parsing each individual XML file stored in the system is not really feasible
when handling a HTTP request from the web frontend, this sort of process would
take a long time to execute. To provide fast search and retrieval of paper
data, a Relational Database Management server (RDBMS) was chosen for storage of
papers that have been preprocessed using the system described above. An
overview of the database schema is illustrated in Figure \ref{fig:e-r-diagram}.

\begin{figure}[th]
\vspace{5mm}
\centering
\includegraphics[width=0.8\textwidth]{images/design/e-r-diagram.png}
\caption{Entity Relationship Diagram for Partridge's RDBMS}
\label{fig:e-r-diagram}
\end{figure}

Partridge's database is required to keep track of all of the papers that have
been added to the system. The Paper entity represents a single paper stored in
Partridge. Information extracted by the classifiers such as the paper's type,
topic and result are stored as part of the main paper entity. The title and
topic are also stored for easy retrieval. One of the key requirements of
Partridge is querying within a CoreSC field of a paper. Therefore, all
sentences are stored as entities along with their CoreSC annotation. The sentence
text is an index field to facilitate fast recall from the database.

It is probable that any given author may have contributed to multiple papers
stored within the system.  Therefore authors are treated as entities within the
RDBMS and the many to many relationship between papers and authors is
facilitated using the intermediary table PaperAuthors. A PaperAuthor record
contains a boolean field used to indicate whether an author linked to a
specific paper was the primary author on that paper.

As discussed above, two or more files per paper are always stored within
partridge so that a user can retrieve them for reading. Therefore files are
kept in their own table along with a record of their type (eg. XML or PDF).

@@

Partridge's web backend component is used to initially serve the HTML and
JavaScript used to represent the User interface and to communicate with the
JavaScript frontend running inside the browser via HTTP requests. It is used to
interpret HTTP request fields into SQL queries and mediate queries made to the
RDBMS on behalf of the user. An example use of the backend system can be seen
in Figure \ref{fig:backend_sequence}.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.75\textwidth]{images/design/backend_sequence.png}
\caption{Sequence Diagram for a Query in Partridge}
\label{fig:backend_sequence}
\end{figure}

The Flask web framework uses a model view controller-like architecture. Each
behaviour of the server: handling paper uploads, displaying paper query
results, allowing users to download papers, can be considered a `view'. Views
register themselves with Flask under a specific URL. When flask receives a
request to any such URL, it automatically routes the request through to the
View object\cite{flask2012}.

\subsubsection{Query View Backend}
The query view is has two key responsibilities. The first is to display the
query form to the user. This is a simple matter of sending an HTML file stored
on the server to the browser that made the request.

The key responsibility of the query view is to translate incoming HTTP requests
into search queries, retrieve a set of papers from the RDBMS  and return human
readable results to the user. One of the most important steps in this process
is to cleanse the incoming data and prevent SQL injection attacks that
unscrupulous users may attempt to use to damage or purge the Partridge
database. The system must also be capable of interpreting data retrieved from
the database into HTML to be returned to the user's browser. The server
mechanism utilises Flask's built in templating mechanism in order to quickly
transform Python-specific data structures into valid HTML markup and return it
to the user\cite{flask2012}.

\subsubsection{Paper Upload View Backend}

The paper upload view backend is responsible for handling file uploads from the
HTML form and ensuring that files are placed in the right place so that the
preprocessor can find them. The main challenge for this submodule is storing
the file using a unique name so that different users uploading files don't
overwrite each other's data. This is handled through the use of the Python UUID
module which generates universally unique 128-bit identifiers as detailed in RFC
4122\cite{rfc4122}. The low rate of collisions between UUID values should
insure that the chances of two paper filenames colliding is very low.

The view also carries out validation on the filename to ensure that it is an
XML or PDF file. No further validation is carried out by this system since the
paper processor carries out file contents inspection and removes invalid file
types automatically.

@@

The web frontend consists of sets of HTML and JavaScript interfaces that are
equipped to communicate with their relevant backend system using

\subsubsection{ Query Form }

\subsubsection{ Results Page }

\subsubsection{ Paper Profile Page }

\subsubsection{Paper Upload Form}
Paper uploading is a

### 2013-03-26 doc/final_report/testing.tex
Made some crucial changes to the testing chapter and worked in intro and summary

@@

Raymond(1999) suggests that as the developer of an open source project,
``Treating your users as co-developers is your least-hassle route to rapid code
improvement and effective debugging\cite{raymond1999cathedral}." Partridge
hasn't been developed using an open methodology since, as a dissertation
project, it has been necessary to avoid complications around work ownership.
However, Raymond's notion that software should be released early and often and
tested on its user-base is an effective one and has been widely adopted by both
open and closed source developers\cite{linux2013}\cite{unity2013}.

As soon as Iteration 1 was complete, Partridge was made open for user testing
and the primary Patridge instance (\url{http://farnsworth.papro.org.uk/}) was
advertised using several social media streams. It was made clear to any early
adopting users that the system was still in development and they were
encouraged to submit bug reports if they experienced any problems whilst using
the site. This was a great success and a number of bugs and suggested
improvements were raised both via the GitHub repository\cite{softlybug2013} and
in conversation, helping to improve Partridge and find some defects that had
previously been overlooked.

@@

Three fold validation is a commonly used method for using all of the available
data for both testing and training whilst still maintaining . As the name
suggests, test data is split into three disjoint sets and then the classifier
is trained on two of the sets and tested with the third. This is repeated three
times so that all sets are used for both training and testing. Results from
each of the folds can be represented separately or an average taken.

@@

3 Fold Validation on the Partridge corpus

@@

ROC charts are often divided into halves diagonally by a line indicating where
the TP-FP ratio is equal. There may be multiple plots on the axes if several
learning algorithms are under evaluation. A graph plot that presents a steep
curve that mostly fits into the upper left half of the graph shows a high TP-FP
ratio which is a sign that the classifier is working well.  Figure
\ref{fig:roc_random_forest} shows the ROC Chart for Partridge's Topic
Classifier after training on 60\% of the Partridge corpus and testing on 40\%.

@@

\caption{Fold 1 Results}
\centering
\begin{tabular}{| l || l | l | l |}
\hline
	&	Case Study&	Research&	Review\\
\hline
\hline
Case Study&	83&		2&		12\\
\hline
Research&	3&		255&		0\\
\hline
Review&		4&		2&		159\\
\hline

@@

\caption{Fold 2 Results}
\centering
\begin{tabular}{| l || l | l | l |}
\hline
&	        Case Study&     Research&	Review\\
\hline
\hline
Case Study&     85    &         2&		10\\
\hline
Research&	0   &		256&		2\\
\hline
Review&		5&		1&		159\\
\hline
\end{tabular}

@@

\caption{Fold 3 Results}
\centering
\begin{tabular}{| l || l | l | l |}
\hline
&		Case Study&	Research&	Review\\
\hline
\hline
Case Study&	82&		3	&	12 \\
Research&	0&		257	&	1\\
Review&		7&		2	&	156\\
\hline
\end{tabular}

@@

>>>>

%introduction to testing
Throughout the implementation of the project, testing has remained a very
important aspect of Partridge's development. A number of testing techniques
have been used in order to evaluate the individual behaviours of Partridge's
key components both separately and the system as a whole. This chapter
discusses the techniques used to test Partridge, the results from these tests
and any implications that these results have had upon development of the
project. Combining all of these testing and evaluation techniques provides an
in depth view of how useful Partridge is and how it can be improved upon.

@@

@@

Three fold validation is a commonly used method for using all of the available
data for both testing and training whilst still maintaining the separation
between training and testing data. As the name suggests, test data is split
into three disjoint sets and then the classifier is trained on two of the sets
and tested with the third. This is repeated three times so that all sets are
used for both training and testing. Results from each of the folds can be
represented separately or an average taken.

@@

3 Fold Validation on the Partridge corpus using the Random Forest Classifier
for paper type gives a CA measure of 87.9\%. While this provides a positive,
general overview of the classifier performance. It does not provide detail on
what data was incorrectly classifier nor any insight on how the system could be
improved. The following sections discuss techniques that provide more useful
measures of performance for machine learning classifiers.

@@

ROC charts are often divided into halves diagonally by a line indicating where
the TP-FP ratio is equal. There may be multiple plots on the axes if several
learning algorithms are under evaluation. A graph plot that presents a steep
curve that mostly fits into the upper left half of the graph shows a high TP-FP
ratio which is a sign that the classifier is working well.  Figure
\ref{fig:roc_random_forest} shows the ROC Chart for Partridge's Paper Type
Classifier after training on 60\% of the Partridge corpus and testing on 40\%.

@@

\caption{Fold 1 Results}
\centering
\begin{tabular}{ | r l l l l |}
\hline
\multirow{5}{*}{\begin{sideways}{Actual Class}\end{sideways}}
&&\multicolumn{3}{c|}{Predicted Class} \\
&& \multicolumn{1}{c}{Case Study} &	Research&	\multicolumn{1}{c|}{Review}\\
\cline{3-5}
& \multicolumn{1}{c|}{Case Study} &	83&		2&		12\\
&\multicolumn{1}{c|}{Research}&	3&		255&		0\\
&\multicolumn{1}{c|}{Review}&	4&		2&		159\\
\hline

@@

\caption{Fold 2 Results}
\centering
\begin{tabular}{ | r l l l l |}
\hline
\multirow{5}{*}{\begin{sideways}{Actual Class}\end{sideways}}
&&\multicolumn{3}{c|}{Predicted Class} \\
&& \multicolumn{1}{c}{Case Study} &	Research&	\multicolumn{1}{c|}{Review}\\
\cline{3-5}
&\multicolumn{1}{c|}{Case Study}&   85    &         2&		10\\
&\multicolumn{1}{c|}{Research}&	0   &		256&		2\\
&\multicolumn{1}{c|}{Review}&	5&		1&		159\\
\hline
\end{tabular}

@@

\caption{Fold 3 Results}
\centering
\begin{tabular}{ | r l l l l |}
\hline
\multirow{5}{*}{\begin{sideways}{Actual Class}\end{sideways}}
&&\multicolumn{3}{c|}{Predicted Class} \\
&& \multicolumn{1}{c}{Case Study} &	Research&	\multicolumn{1}{c|}{Review}\\
\cline{3-5}
&\multicolumn{1}{c|}{Case Study}&	82&		3	&	12 \\
&\multicolumn{1}{c|}{Research}&	0&		257	&	1\\
&\multicolumn{1}{c|}{Review}&		7&		2	&	156\\
\hline
\end{tabular}

@@

Raymond(1999) suggests that for developers of open source projects, ``Treating
your users as co-developers is your least-hassle route to rapid code
improvement and effective debugging\cite{raymond1999cathedral}." Partridge
hasn't been developed using an open methodology since, as a dissertation
project, it has been necessary to avoid complications around work ownership.
However, Raymond's notion that software should be released early and often and
tested on its user-base is an effective one and has been widely adopted by both
open and closed source developers\cite{linux2013}\cite{unity2013}.

A publicly available instance of Partridge that can be accessed at
(\url{http://farnsworth.papro.org.uk/}) was made available as soon as iteration
1 was complete and advertised using several social media streams. This was an
effort to attract as many users to Partridge as possible in the early stages of
the project in order to provide user testing. It was made clear to any early
adopting users that the system was still in development and they were
encouraged to submit bug reports if they experienced any problems whilst using
the site. This was a great success and a number of bugs and suggested
improvements were raised both via the GitHub repository and in conversation,
helping to improve Partridge and find some defects that had previously been
overlooked. For example, one user noticed that the full text search within
Partridge was not behaving as expected and returning all papers regardless of
their contents.  The relevant code was repaired and the bug marked as resolved
on GitHub\cite{softlybug2013}.

\subsection{Intrinsic Feedback}

Intelligent information retrieval using machine learning techniques is a
complicated and multifaceted process. Partridge attempts to encode this complex set of
procedures into a usable and understandable interface designed for the use of
non-programmers. It was therefore important to understand how usable the
interface is for non-technical users.

Most users who commented on the system found that the query form made a lot of
sense and helped them to identify relevant papers very quickly.

There were a few comments on how the uploader system could be improved. Users
were confused by the preprocessor and wondered why their paper didn't appear in
the corpus as soon as they submitted it. The most popular solution to this was
to add an email field to the uploader so that people who submit papers to the
corpus are notified when their paper is incorporated. This also provided
feedback for users whose papers could not be added to the corpus due to errors
or rights ownership issues.

Another suggestion was to add a twitter bot to announce when new papers have
been added to the system. This would provide another way of issuing user
feedback when a paper is submitted and would also help to draw users to
Partridge - especially when high profile papers are successfully added to the
system.

\subsection{Extrinsic Feedback}

As well as finding out how Partridge performs as a system, it was interesting
to find out how Partridge blended in to the information retrieval ecosystem around
it and how effectively it could be used day to day or in combination with any other
online tools.

One of the most important suggestions made was the addition of the Bookmarklet
tool. This had the effect of making paper submission to Partridge a lot more
convenient and intuitive. It also helped reduce confusion over paper
rights since the bookmarklet only works on sites which license
their papers under permissive licenses and allow data mining.

\section{Summary}

The extensive range of testing methodologies used throughout the project meant
that Partridge has been developed into a mature, stable and highly usable
product. Unit testing has ensured that all procedural and scripted
functionality within Partridge is predictable and reliable. Machine Learning
Evaluation has ensured that an accurate and precise paper type classification
mechanism has been developed and User Testing has ensured that non-technical
users are able to use Partridge effectively.

Testing has been highly effective throughout the project and any potential
issues with the system were identified very early on and resolved due to the
`open-source-esque' development lifecycle used during the project.  Testing has
also provided a great deal of understanding about just how useful Partridge is
as well as highlighting its limitations. It also raises questions as to the
future development of the project and provides a number of ideas for future
improvements.
